---
title: 'Homework 4 Answers'
fig-cap: false
---

-   If you find any typos or errors, please feel free to contact me via
    email at r13323002\@ntu.edu.tw. I would appreciate it and will
    correct the solution to prevent any misunderstandings.

-   For some R commands marked with ‘OPTIONAL,’ you don’t need to learn
    them. You will be completely fine on the computer quiz even if you
    choose to ignore them.

-   If you’re having trouble understanding the code, don’t hesitate to
    ask me for help. I’ll do my best to assist you during office hours
    or after the TA session.

``` r
# clear the mamory and import package
rm(list = ls())
library(tidyverse)
read.csv("data/full_body_scan.csv")
```

```{r}
#| echo: false 

# clear the mamory and import package
rm(list = ls())
library(tidyverse)
library(here)

# Import data

body <- read.csv(here("data", "full_body_scan.csv"))
```

## Computer Exercises

### Null and Alternative Hypothesis

$$
\begin{cases}
 H_0&: \text{Answers are independent of party affiliation.}\\
 H_1&: \text{Answers are NOT independent of party affiliation.}
\end{cases}
$$

### Contingency Table and Chi-square Test
``` r
# create two-way table (column percentage)
count_table <- table(body$answer, body$party_affiliation,
                     dnn = c("Asnwer", "Party Affiliation"))
pct_table <- prop.table(count_table, margin = 2)
print(pct_table)

# chi-square test
chi_test <- chisq.test(pct_table)
print(chi_test)
```

```{r}
#| echo: false        # hide code if this is the Answers page

# create two-way table (column percentage)
count_table <- table(body$answer, body$party_affiliation,
                     dnn = c("Asnwer", "Party Affiliation"))
pct_table <- prop.table(count_table, margin = 2)
print(pct_table)

# chi-square test
chi_test <- chisq.test(pct_table)
print(chi_test)
```


### Conclusion

Since the p-value is 0.3598, which is larger than 0.05
, we do not reject the null hypothesis. That is, we don’t have strong evidence that shows an association between answers and party affiliations.

## Textbook Exercise

### Question 6.6
a. With a random sample from < 10% of the population, independence is satisfied. The success–failure condition is also satisfied. Hence, the margin of error can be calculated as follows:

$$
ME \;=\; z^* \sqrt{\frac{p(1-p)}{n}}
\;=\; 1.96 \times \sqrt{\frac{0.66 \times 0.34}{1018}}
\;=\; 0.029 \approx 3\%.
$$

b. A 95% confidence interval for the proportion of adults who think that licensed drivers should be required to re-take their road test once they reach 65 years of age is

$$
0.66 \pm 0.03 \;=\; (0.63,\; 0.69).
$$

Since 70% is not contained in the interval, we would reject a null hypothesis where \(p=0.7\).
Therefore, the data do **not** provide evidence that more than 70% of the population think that drivers over the age of 65 should re-take their road test.

### Question 6.8

a. The population parameter of interest is the proportion of all Greeks who would rate their lives poorly enough to be considered “suffering”, \(p\).
The point estimate for this parameter is the proportion of Greeks in this sample who would rate their lives as such, \(\hat p = 0.25\).

b. Conditions:

1. **Independence:** The sample is random, and \(1000 < 10\%\) of all Greeks, therefore the life rating of one Greek in this sample is independent of another.  
2. **Success–failure:** \(1000 \times 0.25 = 250 > 10\) and \(1000 \times 0.75 = 750 > 10\).  
   Since the observations are independent and the success–failure condition is met, \(\hat p\) is expected to be approximately normal.

c. A 95% confidence interval can be calculated as follows:

$$
\hat p \pm z^* \sqrt{\frac{\hat p(1-\hat p)}{n}}
= 0.25 \pm 1.96 \times \sqrt{\frac{0.25 \times 0.75}{1000}}
= 0.25 \pm 0.0269
= (0.2231,\; 0.2769).
$$

We are 95% confident that approximately 22% to 28% of Greeks would rate their lives poorly enough to be considered “suffering”.

d. Increasing the confidence level would increase the margin of error, hence **widen** the interval.

e. Increasing the sample size would **decrease** the margin of error, hence make the interval **narrower**.

### Question 6.26

a. The hypotheses are

$$
\left\{
\begin{aligned}
H_0 &: \; p_R = p_D \; (\text{Proportions of Republicans and Democrats who support the use of full-body scans are equal.}) \\
H_A &: \; p_R \ne p_D \; (\text{Proportions of Republicans and Democrats who support the use of full-body scans are different.})
\end{aligned}
\right.
$$

The pooled proportion can be calculated as follows:

$$
\hat{p}_{\text{pool}}
= \frac{\text{success}_R + \text{success}_D}{n_R + n_D}
= \frac{264 + 299}{318 + 369}
= \frac{563}{687}
\approx 0.82
$$

Next we calculate the test statistic,

$$
\hat{p}_R=\frac{264}{318}=0.83,\qquad
\hat{p}_D=\frac{299}{369}=0.81
$$

$$
Z
= \frac{\hat{p}_R-\hat{p}_D}
{\sqrt{\hat{p}_{\text{pool}}\,(1-\hat{p}_{\text{pool}})\left(\frac{1}{n_R}+\frac{1}{n_D}\right)}}
= \frac{0.83-0.81}{\sqrt{0.82\times 0.18\left(\frac{1}{318}+\frac{1}{369}\right)}}
= \frac{0.02}{0.0294}
= 0.68
$$

and the p-value:

$$
p-\text{value}
= P\big(|\hat{p}_R-\hat{p}_D|>0.02 \mid H_0\big)
= P(|Z|>0.68)
= 2 \times 0.2483
= 0.4966
$$

Since the p-value is high, we fail to reject $H_0$. The data do not provide strong evidence that the proportions of Republicans and Democrats who support the use of full-body scans are different.

b. We may have made a Type II error, since we may have incorrectly failed to reject $H_0$.


### Question 6.40

a. Multiply each percent by 701:

|            | Download | No Download |
|------------|:--------:|:-----------:|
| Positions 1|    97    |     128     |
| Positions 2|   102    |     130     |
| Positions 3|    85    |     159     |



b. **Prepare.** It is convenient to construct the actual table we care about, which will represent the totals in the three experiment groups:

| Group       | Total |
|-------------|:-----:|
| Positions 1 |  225  |
| Positions 2 |  232  |
| Positions 3 |  244  |

This now looks like a goodness of fit chi-square problem. As part of our *Prepare* step, we should also construct the hypotheses.

$$
\left\{
\begin{aligned}
H_0 &: \text{ The chance a user is in any experiment group is equal among the three groups.}\\
H_A &: \text{ The chance of being in one group or another varies by the group.}
\end{aligned}
\right.
$$

**Check.** If $H_0$ were true, then we’d expect $1/3$ of the 701 visitors to be in each group, i.e. $233.67$ in each group. The $233.67$ is greater than 5 for all three groups, satisfying one of the required conditions. The independence condition is also satisfied since each visitor was randomly assigned to a group and only counted once in the table. With the conditions satisfied, we can move forward with conducting a goodness-of-fit chi-square test.

**Calculate.** We can compute the test statistic and degrees of freedom:

$$
\chi^2
= \frac{(255-233.67)^2}{233.67}
+ \frac{(232-233.67)^2}{233.67}
+ \frac{(244-233.67)^2}{233.67}
= 0.79
$$

$$
df = 3-1 = 2
$$

Using software, we can identify the tail area as $0.67$.

**Conclude.** Because the p-value is larger than $0.05$, we do not reject $H_0$. That is, we do not see any evidence that visitor randomization to the groups is imbalanced / malfunctioning.

---

c. **Prepare.**

$$
\left\{
\begin{aligned}
H_0 &: \text{ No difference in download rate across the experiment groups.}\\
H_A &: \text{ There is some difference in download rate across the groups.}
\end{aligned}
\right.
$$

**Check.** Each visitor was randomly assigned to a group and only counted once in the table, so the observations are independent. The expected counts can also be computed by constructing row and column totals, then multiplying these (and dividing by the table total) to get the expected counts under $H_0$. Those expected counts are (reading down the first column then down the second): 91.2, 94.0, 98.9, 133.8, 138.0, 145.2. All of these expected counts are at least 5. Therefore, we can use the chi-square test.

**Calculate.** We can calculate the test statistic as

$$
\chi^2
= \frac{(97-91.2)^2}{91.2}
+ \cdots
+ \frac{(159-145.2)^2}{145.2}
= 5.04
$$

with $df=(3-1)\times(2-1)=2$. This results in a p-value of $0.08$, which we can find using software.

**Conclude.** Because the p-value is less than $0.05$, we do not reject $H_0$. That is, we have not found evidence that there is any difference in the download rate depending on the download link position.

### Question 6.42

a. The hypotheses are as follows:

$$
\left\{
\begin{aligned}
H_0 &: p = 0.5 \ \ (50\% \text{ of Americans think the Civil War is still relevant})\\
H_A &: p \ne 0.5 \ \ (\text{A majority of Americans hold an opinion (for or against) that the Civil War is still relevant.})
\end{aligned}
\right.
$$

Before calculating the test statistic we should check that the conditions are satisfied:

1. **Independence:** The sample is random, and 1,507 $<10\%$ of all Americans, therefore whether or not one American in the sample thinks the Civil War is still relevant is independent of another.  
2. **Success-failure:** $1,507 \times 0.50 = 753.5 > 10$ and $1,507 \times 0.50 = 753.5 > 10$. Since the observations are independent and the success-failure condition is met, $\hat{p}$ is expected to be approximately normal.

The test statistic and the p-value can be calculated as follows:

$$
Z = \frac{\hat{p}-p_0}{\sqrt{\dfrac{p_0(1-p_0)}{n}}}
= \frac{0.56-0.5}{\sqrt{\dfrac{0.5\times 0.5}{1{,}507}}}
= \frac{0.06}{0.0129}
= 4.65
$$

$$
p\text{–value} = P(\hat{p} > 0.56 \mid p=0.5) = P(|Z|>4.65) \approx 0
$$

Since the p-value is very small, we reject $H_0$. Since the data show $\hat{p} > 0.5$ and we’ve rejected $H_0$, the data provide strong evidence that the majority of the Americans think the Civil War is still relevant.

b. If in fact only $50\%$ of Americans thought the Civil War is still relevant, the probability of obtaining a random sample of $1,507$ Americans where $56\%$ or more think it is still relevant would be approximately $0$.

c. First we need to recheck the success-failure condition using the sample proportion:  
$1,507 \times 0.56 = 843.92 > 10$ and $1,507 \times 0.44 = 663.08 > 10$. A $90\%$ confidence interval can be calculated as follows:

$$
\hat{p} \pm z^\star \sqrt{\frac{\hat{p}(1-\hat{p})}{n}}
= 0.56 \pm 1.65 \sqrt{\frac{0.56\times 0.44}{1{,}507}}
$$

$$
= 0.56 \pm 1.65 \times 0.0128
= 0.56 \pm 0.02
= (0.54,\; 0.58)
$$

We are $90\%$ confident that $54\%$ to $58\%$ of all Americans think that the Civil War is still relevant. This agrees with the conclusion of the earlier hypothesis test since the interval lies above $50\%$.

### Question 6.50

a. Chi-squared test of independence.

b. The hypotheses are:

$$
\left\{
\begin{aligned}
H_0 &: \text{Caffeinated coffee consumption and depression in women are independent.}\\
H_A &: \text{Caffeinated coffee consumption and depression in women are dependent/associated.}
\end{aligned}
\right.
$$

c. Depression: $\dfrac{2607}{50739}=0.0514$

\quad No depression: $1-0.0514=0.9486$

d. We have:

$$
E=\frac{2607 \times 6617}{50739}=339.9854 \approx 340
$$

$$
\frac{(O-E)^2}{E}=\frac{(373-340)^2}{340}=3.20
$$

e. $\text{df}=(R-1)\times(C-1)=1\times 4=4$, and $p$-value $<0.001$.

f. The $p$-value is small and we reject $H_0$. The data provide convincing evidence to suggest that caffeinated coffee consumption and depression in women are associated.

g. Yes, this is an observational study. Based on this study we can’t deduce that drinking more coffee leads to less depression. There may be other factors, lurking variables, that cause decreased depression in women who drink more coffee.
