---
title: 'Week 2 Answers (0909)'
fig-cap: false
---


## Download Data

Please download the datasets `county.csv` and `loan50.csv` [here](https://www.openintro.org/data/){target="_blank"}.

## Import Data

1.  Import the package `tidyverse`, which contains several useful functions for data wrangling and visualization.

2.  Create a folder on your computer to store the dataset downloaded from NTU COOL or OpenIntro website.\
    Set your working directory as that folder and import the datasets `county.csv` and `loan50.csv`.

``` r
library(tidyverse)
setwd("/your/working/directory")
county <- read.csv("county.csv")
loan <- read.csv("loan50.csv")
```

## Scatter Plot

1.  Use `county.csv` to draw the scatter plot of `unemployment_rate` (x-axis) and `per_capita_income` (y-axis).

:::{.callout-tip title="Hint"}
**Hint:** You don’t need to specify any parameter in `geom_point()`.
:::

``` r
ggplot(county, aes(x = unemployment_rate, y = per_capita_income)) + 
  geom_point()
```

```{r}
#| label: scatter
#| fig-width: 8       # inches
#| fig-height: 5
#| out-width: "90%"   # scales in the page
#| fig-align: center
#| echo: false        # hide code if this is the Answers page

library(ggplot2)
library(here)
county <- read.csv(here("data", "county.csv"))
ggplot(county, aes(unemployment_rate, per_capita_income)) +
  geom_point()
```

2.  Draw the same graph again, but this time make the following adjustments:

    -   adjust the point color to `lightcoral`
    -   adjust the point size to `0.5`

``` r
ggplot(county, aes(x = unemployment_rate, y = per_capita_income)) +
  geom_point(color = "lightcoral", size = 0.5)
```

```{r}
#| label: scatter-colored
#| fig-width: 8       # inches
#| fig-height: 5
#| out-width: "90%"   # scales in the page
#| fig-align: center
#| echo: false        # hide code if this is the Answers page

ggplot(county, aes(unemployment_rate, per_capita_income)) +
  geom_point(color = "lightcoral", size = 0.5)
```

## Histogram

Use `loan50.csv` data to draw the histogram of `loan_amount` (set as x-axis), and adjust the parameter `binwidth` in `geom_histogram()` to 5000.

``` r
ggplot(loan, aes(x = loan_amount)) +
  geom_histogram(binwidth = 5000)
```

```{r}
#| label: hist-loan
#| fig-width: 8
#| fig-height: 5
#| out-width: "90%"
#| fig-align: center
#| echo: false
loan   <- read.csv(here("data", "loan50.csv"))
ggplot(loan, aes(x = loan_amount)) +
  geom_histogram(binwidth = 5000)
```
