---
title: 'Week 4 Answers (0923)'
fig-cap: false
---


## Project

Remember to use the project you create last week!

## Draw Uniform Random Sample

Set random seed as 2025. Draw 200 observations from uniform distribution [0, 100] and compute the mean of the observations.

::: {.callout-tip title="Hint"}
**Hint:** Use `mean()` function.
:::

``` r
set.seed(2025)
sample_size <- 200
rdn <- runif(n = sample_size, min = 0, max = 100)
mean <- mean(rdn)
print(mean)
```

``` r
## [1] 52.17858
```

```{r}
#| echo: false        # hide code if this is the Answers page

rm(list = ls())
set.seed(2025)
sample_size <- 200
rdn <- runif(n = sample_size, min = 0, max = 100)
```

## Histogram

1. Using the random sample you just generated, create a DataFrame to store the drawn values by using `data.frame()` function, and draw the histogram graph to see the distribution.

``` r
df_1 <- data.frame(
  values = rdn
)
ggplot(df_1, aes(x = values)) +
  geom_histogram()
```

```{r}
#| fig-width: 8       # inches
#| fig-height: 5
#| out-width: "90%"   # scales in the page
#| fig-align: center
#| echo: false        # hide code if this is the Answers page

library(ggplot2)
df_1 <- data.frame(
  values = rdn
)
ggplot(df_1, aes(x = values)) +
  geom_histogram()
```

2. Now, draw another 10,000 observations from uniform distribution [0, 100], and draw the histogram graph to see the distribution.


``` r
rdn_2 <- runif(n = 10000, min = 0, max = 100)
df_2 <- data.frame(
  values = rdn_2
)
ggplot(df_2, aes(x = values)) +
  geom_histogram()
```

```{r}
#| fig-width: 8       # inches
#| fig-height: 5
#| out-width: "90%"   # scales in the page
#| fig-align: center
#| echo: false        # hide code if this is the Answers page

rdn_2 <- runif(n = 10000, min = 0, max = 100)
df_2 <- data.frame(
  values = rdn_2
)
ggplot(df_2, aes(x = values)) +
  geom_histogram()
```