---
title: 'Week 14 Answers (1202)'
fig-cap: false
---


## Reminders

1. Remember to use the project and create a new script in your script folder!

2. Better to use only the functions taught in the course.


## Download Data

Please download the datasets `nba_players_19.csv` and `gpa_iq.csv` [here](https://www.openintro.org/data/){target="_blank"}.


## ANOVA

### ANOVA Testing

Use the `aov()` function to perform an ANOVA test to determine if there is no difference in height among players in each position group. Then, use the `summary()` function to obtain the p-value and make a conclusion. 

```r
aov_result <- aov(nba$height ~ nba$position)
summary(aov_result)
```

```{r}
#| echo: false        # hide code if this is the Answers page
rm(list = ls())
library(tidyverse)
library(here)

nba <- read.csv(here("data", "nba_players_19.csv"))

aov_result <- aov(nba$height ~ nba$position)
summary(aov_result)
```
We reject the null hypothesis, which states that there is no difference in height among position groups. This indicates that the height of a player is significantly associated with their position.

## Linear Regression

### Correlation Coefficient
Using the `gpa` dataset, use the `summarize()` function to compute the standard deviation of `gpa`, the standard deviation of `iq`, and the correlation coefficient between `gpa` and `iq`.


::: {.callout-tip title="Hint"}
Use `cor(x, y)` to compute the correlation coefficient between the variables `x` and `y`.
:::

```r
gpa %>% summarize(
    sd_gpa = sd(gpa),
    sd_iq = sd(iq),
    cor = cor(gpa, iq)
  )
```


```{r}
#| echo: false        # hide code if this is the Answers page

gpa <- read.csv(here("data", "gpa_iq.csv"))

gpa %>% summarize(
    sd_gpa = sd(gpa),
    sd_iq = sd(iq),
    cor = cor(gpa, iq)
  )
```


### Regression

Now suppose `gpa` is the outcome (dependent variable), and `iq` is the explanatory (independent variable). Use the `lm()` function to predict `gpa` based on `iq`. In other words, fit a linear model to estimate the relationship between `gpa` and `iq`.


```r
lm_model <- lm(gpa$gpa ~ gpa$iq)
summary(lm_model)$coefficient
```


```{r}
#| echo: false        # hide code if this is the Answers page

gpa <- read.csv(here("data", "gpa_iq.csv"))

lm_model <- lm(gpa$gpa ~ gpa$iq)
summary(lm_model)$coefficient
```


## Regression with Plot

Lastly, let’s visualize the linear regression on a scatter plot. Create the plot with the following specifications:

- Use the `ggplot()` and `geom_point()` function to create a scatter plot, with the x-axis representing `iq` and the y-axis representing `gpa`.

- Use the `geom_smooth()` function to add a fitted line based on a linear model.

```r
ggplot(gpa, aes(x = iq, y = gpa)) +
  geom_point() +
  geom_smooth(method = "lm", se = TRUE)
```


```{r}
#| echo: false        # hide code if this is the Answers page

ggplot(gpa, aes(x = iq, y = gpa)) +
  geom_point() +
  geom_smooth(method = "lm", se = TRUE)
```
